---
title: "teste_shiny"
author: "tiago"
date: "19 de setembro de 2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(extrafont)
library(kableExtra)
library(lubridate)
library(gganimate)
library(scales)
library(ggrepel)
library(xts)
library(dygraphs)
loadfonts()
```


```{r}
dados_CxLiq_Siafi <- read_excel("data/MCTI_lim_saque_liq_pagar.xlsx", skip = 5)

colnames(dados_CxLiq_Siafi) <- c(
  "codOrgao", 
  "nomeOrgao", 
  "Data", 
  "Item", 
  "Movimento")

dados_CxLiq <- dados_CxLiq_Siafi %>%
  filter(!(codOrgao %in% c("49280", "20502"))) %>% # (1)
  mutate(Date     = if_else(str_sub(Data, 1, 4) == "000/", 
                            as.Date(paste0(str_sub(Data, 5, 8),"-01-01")),
                            dmy(Data))) %>%
  group_by(Date, codOrgao, Item) %>% 
  summarise(Movimento = sum(Movimento)) %>%
  ungroup() %>%
  unite(classificador, Item, codOrgao, sep = "__") %>% # (2)
  select(Date, classificador, Movimento) %>%
  spread(key = classificador, value = Movimento, fill = 0) %>%
  complete(Date = seq(min(Date), max(Date), by = "days")) %>% # (3)
  replace(is.na(.), 0) %>%
  mutate_at(-1, funs(cumsum(.))) %>% # (4)
  mutate(data_num = factor(paste0(year(Date), # (5)
                                  str_sub(Date, 6, 7), 
                                  str_sub(Date, 9, 10)))) %>%
  gather(c(-"data_num", -"Date"), key = classificador, value = coluna) %>%
  separate(classificador, c("item", "codOrgao"), sep = "__") %>%
  spread(key = item, value = coluna, fill = 0) %>%
  rename(Caixa      = `LIMITES DE SAQUE (OFSS, DIVIDA, BACEN E PREV)`,
         Obrigacoes = `VALORES LIQUIDADOS A PAGAR (EXERCICIO + RP)`) %>%
  mutate(Saldo      = Caixa - Obrigacoes)
```

Gera lista de xts's

```{r}

lista_orgaos <- unique(dados_CxLiq$codOrgao)

gera_xts <- function(orgao) {
  dados_xts <- dados_CxLiq %>% 
        filter(codOrgao == orgao) %>%
        select(Date, Caixa, Obrigacoes, Saldo) %>%
        mutate_at(-1, funs(./1000000))
  sh_xts <- xts(dados_xts[,-1], order.by = dados_xts$Date)
}

lista_xts <- lapply(lista_orgaos, gera_xts)
names(lista_xts) <- lista_orgaos


# gerar um total
xts_total <- lista_xts[[1]]
for (i in 2:length(lista_xts)) {
  xts_total <- xts_total + lista_xts[[i]]
}

xts_total_semAnatel <- xts_total - lista_xts[["41231"]]

lista_xts[[length(lista_xts)+1]] <- xts_total_semAnatel
lista_xts[[length(lista_xts)+1]] <- xts_total

lista_orgaos <- c(lista_orgaos, "Total sem Anatel", "Total")
names(lista_xts) <- lista_orgaos

# para conferir

head(xts_total)

dados_CxLiq %>% 
  filter(Date <= "2017-01-06") %>% 
  group_by(Date) %>% 
  summarise_at(c("Caixa", "Obrigacoes", "Saldo"), sum)

cores <- RColorBrewer::brewer.pal(3, "Set2")
nomes_series <- c("Caixa", "Obrigacoes", "Saldo")
names(cores) <- nomes_series

```



This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("orgao", label = "Órgão do MCTI:",
              choices = lista_orgaos, selected = lista_orgaos[1]),
  radioButtons("periodicidade", label = "Periodicidade", 
               choiceNames = c("Diários", "Semanais", "Mensais"),
               choiceValues = c("days", "weeks", "months"),
               selected = "days"),
  checkboxGroupInput("variavel", label = "Série", 
                     choiceNames  = c("Caixa", "Obrigações", "Saldo"),
                     choiceValues = c("Caixa", "Obrigacoes", "Saldo"),
                     selected     = c("Caixa", "Obrigacoes", "Saldo"))
)

renderDygraph({
  
  xts_selecionado <- lista_xts[[input$orgao]][endpoints(lista_xts[[input$orgao]], on = input$periodicidade), # (1)
                                              input$variavel]
  
  # xts_selecionado <- lista_xts[[input$orgao]]
  
  dygraph(xts_selecionado) %>%
      dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2"),
                drawAxesAtZero = TRUE) %>%
      dyHighlight(highlightCircleSize = 5,
                  highlightSeriesBackgroundAlpha = 0.4,
                  highlightSeriesOpts = list(strokeWidth = 3),
                  hideOnMouseOut = FALSE) %>%
      dyAxis("y",
             label = "R$ milhões",
             pixelsPerLabel = 40,
             gridLineColor = "rgb(222,222,222)",
             axisLineColor = "white",
             valueFormatter = "function(y) {
                  return 'R$' + y.toFixed(2) + ' mi';
                }") %>%
      dyAxis("x",
             pixelsPerLabel = 40,
             gridLineColor = "rgb(222,222,222)",
             rangePad = 5,
             axisLineColor = "rgb(24,24,24)") %>%
      dyLegend(show = "always") %>%
      dyRangeSelector()
})

#       dyLimit(0, color = "") %>%
# (1) para indexar o xts desejado na lista de xts, usa-se, por exemplo lista_xts[[1]].
#     para selecionar uma coluna específica desses xts, usa-se, por exemplo lista_xts[[1]][,1] (ele não considera as datas como coluna, mind you)
#
# então, esse código faz o seguinte:
#
# lista_xts[[indexador]] : seleciona o xts desejado, conforme a seleção do usuário
# lista_xts[[indexador]][, coluna] : seleciona a coluna desejada do xts desejado, conforme seleções
# lista_xts[[indexador]][vetor_de_datas, coluna] : seleciona a coluna desejada do xts desejado para as datas desejadas, conforme o resultado da função "endpoints" a partir da seleção do usuário
#
# para fixar as cores: dySeries("Caixa", color = cores[1]). mas aí a seleção de series não funciona.
```

